\begin{appendices}

% e.g., User Manuals, supporting evidence for claims made in the main part of the dissertation (e.g. a copy of a user evaluation questionnaire), samples of test data, etc. Note that Appendices are optional.


\chapter{Computational Code}
Some Code snippets that includes the few logical functionalities of the application for review as below.

Some backend service classes in Java Springboot which performs the logical programming part.

User Feed service class where the algorithm works gathering categories and updating respective weights and updating user category-weight map.

\lstinputlisting[firstline=20,lastline=75,title = UserFeed Service,language=java ]{code/UserFeedService.java}

User feed service fetching personalized news feed based on ranking with weights and filtering in algorithm.
\lstinputlisting[firstline=161,lastline=208,title = UserFeed Service ]{code/UserFeedService.java}
\lstinputlisting[firstline=14,lastline=38, title = News Service]{code/DNewsService.java} 

Below Springboot startup code runs the springboot application and also performs conversion of json news objects to database objects using Command line runner.
\lstinputlisting[firstline=28,lastline=56,title = SpringBoot application startup ]{code/ProjectApplication.java}

Sample Controller classes to explain api calls at backend.

Login Controller with JWT token generation code

\lstinputlisting[firstline=12,lastline=50, title = Login Controller ]{code/LoginController.java} 

User Feed Controller where it recommends user-user similarity of interests based articles.
\lstinputlisting[firstline=135,lastline=197, title = UserFeed Controller ]{code/UserFeedController.java} 

JPA Native query fetching required news data based on parameters.
\lstinputlisting[firstline=17,lastline=38, title = News Repository ]{code/DNewsRepository.java} 

Security Configuration in Springboot
\lstinputlisting[firstline=22,lastline=67, title = Spring Security  ]{code/SecurityConfig.java} 

Frontend Code to display data in the client accomplished with Angular, HTML, bootstrap, CSS.

Globe data showing specified country information and category filter in addition to country achieved using amcharts and Behavioral Subjects in angular.
\lstinputlisting[firstline=20,lastline=217, title = Global Visulization,language=java]{code/globaldata.component.ts} 

User Profile with user data is displayed and editable in frontend with category weight in pie-charts visualization.
\lstinputlisting[firstline=16,lastline=141, title = User Profile and chart Visualization]{code/user-profile.component.ts} 

Evaluation performed with Test Driven development and sample test case snippets.
Sample User add, find and update testcases.
\lstinputlisting[firstline=24,lastline=123, title = User Testcases]{code/UserControllerTest.java} 

Userfeed Controller tests that verifies all the interactions are working as expected with assert conditions.

\lstinputlisting[firstline=41,lastline=142, title = User Feed Testcases]{code/UserFeedControllerTest.java} 
\end{appendices}