\cleardoublepage

\addcontentsline{toc}{chapter}{Acknowledgements}

\begin{acknowledgements}

I would like to thank my Supervisors Dr.John Panneerselvam and Dr.Ulidowski, Irek for providing guidance and support throught the project. The ideas and approach provided by Professor John was very helpful to develop the application according to the software development cycle. And the inputs from Professor Irek during the meeting gave a clear picture of the how the project report should come up and also to do some enhancements in the application. And a sincere thanks to Dr. John Drake who organized our master project conducting up-to-date guidance sessions and cleared our queries throughout the dissertation.

Also, I would like to extend my acknowledge to my parents and my sister who constantly supported to achieve my goals throughout the university.



\begin{center}
  \normalsize\bfseries\MakeUppercase{DECLARATION}
\end{center}

All sentences or passages quoted in this report, or computer code of any form whatsoever used and/or submitted at any stages, which are taken from other people’s work have been specifically acknowledged by clear citation of the source, specifying author, work, date and page(s). Any part of my own written work, or software coding, which is substantially based upon other people’s work, is duly accompanied by clear citation of the source, specifying author, work, date and page(s). I understand that failure to do this amount to plagiarism and will be considered grounds for failure in this module and the degree examination as a whole.\newline

\textbf{Name: Sittukala Saravanan} \newline
\textbf{Date: 10/09/2021}

\end{acknowledgements}