\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}

Personalized Buzzfeed is a simple user-friendly news feed desktop application with responsive designs which is developed for the users to login and read news around the globe. The application is designed considering three major features which includes Personalization, Visualization and Recommendation. Personalization is more important in any web application to keep the users around. But Visualization helps them to feel interactive and keep engaged. Additionally Recommendation helps users to understand their preferences much better and explore the application with the suggestions. In this project, Personalization is approached with few ideas from both Contextual and Behavioral aspects and Visualization is represented using amcharts chart and map projections with Recommendations using the Apache Mahout Recommendation Model which is a machine-learning framework. So, the application is designed to develop all these features at its possibly the best first version which still can refined and enhanced in the future to a business product.\newline
The project development is aligned with SMART goals which makes it achieve the project standards set by the university at the first level and the industry in the future\cite{mchale_2021}. \textbf{SMART} is an acronym that means Specific, Measurable, Achievable, Realistic and Time-bound.\newline
\begin{itemize}
    \item \textbf{Specific} - The requirements were determined and documented in the preliminary report and was not deviating in the project.
    \item \textbf{Measurable} - The project progress were monitored periodically and tracked in the interim report which provided targets achieved and the tasks yet to achieve.
    \item \textbf{Achievable} - The interim report made clear the pending tasks and feasibility of achieving them as agreed. 
    \item \textbf{Realistic} - The requirements had been done feasibility check by background analysis through research papers and going through conceptual ideas and made clear.
    \item \textbf{Time-bound}  - Timely delivery of the reports and code components had been performed to meet the respective deadlines. \newline
    
    Achieving this overall goals to almost 80-90\% helped the project go through various stages of development and testing efficiently and reach the desired results.
\end{itemize}

The project is evaluated through various types of testing. From the front end user perspective and achieving the stakeholders requirements, \textbf{Usability} testing was carried out and from the back-end to assess all the functionalities, \textbf{Test Driven Development} (TDD) which covers Junit testcases has been written and successfully passed all the testcases.

\end{abstract}